Breadth First Searches Over Evolving Graphs

### 2016-01-23 paper.tex
Better title and abstract

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{An Algorithm for Searching Evolving Graphs in Linear Algebraic Language}

@@

\author{
\IEEEauthorblockN{Jiahao Chen}
\IEEEauthorblockA{ Computer Science and Artificial Intelligence Laboratory,\\
Massachusetts Institute of Technology,\\
Massachusetts, 02139-4307,USA\\
jiahao@mit.edu}
\and
\IEEEauthorblockN{Weijian Zhang}
\IEEEauthorblockA{School of Mathematics,\\
University of Manchester,\\
Manchester, M13 9PL, England\\
weijian.zhang@manchester.ac.uk}
}

@@

\begin{abstract}
  % A generalization of the breadth-first search (BFS) algorithm on evolving graphs is
  % discussed.
  % The representation of this algorithm
  % as algebraic operations is investigated.
  % The duality of the vector-matrix multiplication
  % and a BFS step is extended to the fact that a block vector-matrix multiplication
  % is dual with the evolving-graph BFS.
  % It is found that the algebraic representation allows for flexible forward and backward searching and can be used for mining citation networks.
A generalized breadth-first search (BFS) algorithm is presented for
searching evolving graphs.
The method is described in both graph and linear algebra notation and
the two algorithms are shown to be equivalent.
A preliminary discussion on mining citation networks is also presented.
\end{abstract}

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Breadth First Searches Over Evolving Graphs}

@@

\author{
\IEEEauthorblockN{Jiahao Chen}
\IEEEauthorblockA{Computer Science and Artificial Intelligence Laboratory,\\
Massachusetts Institute of Technology,\\
Cambridge, Massachusetts, 02139-4307, USA\\
jiahao@mit.edu}
\and
\IEEEauthorblockN{Weijian Zhang}
\IEEEauthorblockA{School of Mathematics,\\
University of Manchester,\\
Manchester, M13 9PL, England, UK\\
weijian.zhang@manchester.ac.uk}
}

@@

\begin{abstract}
We present a generalization of the breadth first search (BFS) algorithm on
evolving graphs and prove its correctness. The BFS generates paths with nontrivial
structure, which we term temporal paths. We also show with simple counterexamples
that simple products of adjacency matrices do not have the correct combinatorial
properties of enumerating temporal paths. On the contrary, the correct generalization
of BFS requires careful tracking of active nodes which participate in the definition
of edges at specific times. We discuss how the structure of temporal paths leads
to nontrivial matrix structure in adjacency matrix representations of evolving
graphs, as well as implications for real world applications
such as the analysis of citation networks.
\end{abstract}
